Reading dataframe
```{r}
dados <- read.csv("tempo.csv", sep = ";", na.strings = "", stringsAsFactors = TRUE)
summary(dados)
View(head(dados))
View(tail(dados))
```

Renaming columns
```{r}
colnames(dados) <- c("Weather", "Temperature", "Humidity", "Wind", "PlayGame")
colnames(dados)
```
Exploring Weather Rows - Wrong Weather Factor (1)
```{r}
summary(dados$Weather)
dados$Weather <- as.character(dados$Weather)
dados$Weather[dados$Weather == "sol"] <- "Sunny"
dados$Weather[dados$Weather == "nublado"] <- "Cloudy"
dados$Weather[dados$Weather == "chuva"] <- "Rainy"
dados$Weather <- factor(dados$Weather)
```
Exploring Temperature Data - 130 ~ 130 F | Outlier (1)
```{r}
View(head(dados))
counts <- table(dados$Temperature)
counts
summary(dados$Temperature)
boxplot(dados$Temperature, outline = FALSE)
hist(dados$Temperature)
```
Exploring Humidity Data - 0 ~ 100 | NA's (1), Outlier (1)
```{r}
summary(dados$Humidity)
boxplot(dados$Humidity)
hist(dados$Humidity)
```
Exploring Wind Data - NA's (1)
```{r}
summary(dados$Wind)
```
Exploring PlayGame Data
```{r}
summary(dados$PlayGame)
dados$PlayGame <- as.character(dados$PlayGame)
dados$PlayGame[dados$PlayGame == "sim"] <- "Yes"
dados$PlayGame[dados$PlayGame == "nao"] <- "No"
dados$PlayGame <- factor(dados$PlayGame)
dados$PlayGame
```
Data Cleaning - Weather | Wrong Weather Factor (1) | two modals -> decision: remove
```{r}
unique(dados$Weather)
summary(dados$Weather)
dados <- subset(dados, Weather %in% c("Sunny", "Cloudy", "Rainy"))
dados$Weather <- factor(dados$Weather)
```
Data Cleaning - Temperature | Outlier | Max Value: 130 (1)
```{r}
summary(dados$Temperature)
dados$Temperature[dados$Temperature > 130] <- median(dados$Temperature, na.rm = TRUE)
```
Data Cleaning - Humidity | Outlier (1) | Max Value: 100
```{r}
summary(dados$Humidity)
dados$Humidity[dados$Humidity > 100] <- median(dados$Humidity, na.rm = TRUE)
dados <- dados[!is.na(dados$Humidity), ]
```